Methods Power Study

### 2022-08-12 manuscript_draft.Rmd
updating with new simulation code

*Samples*. Each population was then sampled as if a researcher was conducting a pilot study. The sample sizes started at 20 participants per item increasing in units of 5 up to 100 participants.

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 2000 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams or have participant funds; however, the sample size simulations were estimated over this amount to determine the pattern of suggested sample sizes (i.e., the function between original sample size and proposed sample size). The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

@@

In this procedure, we identified three points of simulation: the population, the samples from those populations, and the researcher sample simulation. In order to minimize any potentially random quirks, we ran each of these samples 100 times for a total of 1000000 simulations. The average of these simulations is presented in the results.

@@

```{r import-data}

>>>>

*Samples*. Each population was then sampled as if a researcher was conducting a pilot study. The sample sizes started at 20 participants per item increasing in units of 10 up to 100 participants.

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming each pilot sample represents a dataset a researcher has collected, we will simulate samples of 20 to 2000 increasing in units of 20 to determine what the new sample size suggestion would be. We assume that samples over 500 may be considered too large for many researchers who do not work in teams or have participant funds; however, the sample size simulations were estimated over this amount to determine the pattern of suggested sample sizes (i.e., the function between original sample size and proposed sample size). The standard error of each item was calculated for each suggested sample size by pilot sample size by population type.

@@

In order to minimize any potentially random quirks, we simulated the sample selection from the population 100 times and the researcher simulation 100 times for each of those selections, resulting in 10000 simulations of all combinations of variables (i.e., scale of the data, heterogeneity, pilot study size, researcher simulation size). The average of these simulations is presented in the results.

@@

```{r import-data}
summary_long <- import("simulation_study/simulated_summary_data.csv")
```

### 2022-08-12 simulation_study/simulate_summary.Rmd
updating with new simulation code

```{r simulation_pipeline, include = T, echo = T}
# a list to save this in 
full_simulation <- list()

for (i in 1:10){

  # simulate population 
  populations <- simulate_population(x)

  for (p in 1:10){

    # simulate samples from population
    samples <- simulate_samples(start = 20, stop = 100, increase = 5, 
                            population1 = populations$population1,
                            population2 = populations$population2, 
                            population3 = populations$population3)

@@

@@

    for (q in 1:10){

      # simulate researcher
      researcher_data <- simulate_researcher(samples1 = samples$samples1, 
                                       samples2 = samples$samples2,
                                       samples3 = samples$samples3, 
                                       start = 20, stop = 30, 
                                       increase = 5)

@@

    } # tell the researcher to do it 1000 times for normal simulation numbers

    # after the researcher summary, summarize and stick in dataframe 
    # so we have a dataframe of each population by sample 
    full_simulation[[paste(i, "_", q, sep = "")]] <- 
      bind_rows(researcher_summary) %>% 
      group_by(scale, original_n, source, name, power) %>% 
      summarize(sample_size = mean(sample_size),
                value = mean(value), .groups = "keep")

  } # simulate the sample 100 times for each population

} # simulate the population 100 times

```

>>>>

```{r simulation_pipeline, include = T, echo = T}
# a list to save this in 
full_simulation <- list()
populations <- simulate_population(x)

for (p in 1:100){

  # simulate samples from population
  samples <- simulate_samples(start = 20, stop = 100, increase = 10, 
                          population1 = populations$population1,
                          population2 = populations$population2, 
                          population3 = populations$population3)

@@

  cat(paste(p, Sys.time(), "\n"))

@@

  for (q in 1:100){

    # simulate researcher
    researcher_data <- simulate_researcher(samples1 = samples$samples1, 
                                     samples2 = samples$samples2,
                                     samples3 = samples$samples3, 
                                     start = 20, stop = 2000, 
                                     increase = 20)

@@

  } # researcher 100 simulations

  # after the researcher summary, summarize and stick in dataframe 
  # so we have a dataframe of each population by sample 
  full_simulation[[paste(p, Sys.time(), sep = "_")]] <-
   bind_rows(researcher_summary) %>%
   group_by(scale, original_n, source, name, power) %>%
   summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")

  # writing out takes time but don't want to lose 100 researcher sims
  # ran this across computers so make clear when run 
  saveRDS(full_simulation, file = paste("simulation_", Sys.time(), ".Rdata", sep = ""))

} # simulate sampling 100 times from the population
```
